\propertitle

### 2019-12-03 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-03T09:50:35+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The second point is that our degrees of belief about the frequency
distribution for the larger population depend not only on the measured data in
the sample, but also on our pre-data beliefs $\yI$ about the distribution.
Which assumptions lead to the maximum-entropy result? This distribution
appears when our initial belief about the possible frequency distributions
$\yF$ is quantified by an entropic prior
\citep{neumann2007,rodriguez1991,skilling1998,catichaetal2004,portamana2017}:
\begin{equation}
  \label{eq:entropic_prior}
  \pf(\yF \| \yI) \propto  \exp[-\yL\;\re(\yF;\yR)]
  \approx \binom{L}{L\yFF_{0}, \dotsc, L\yFF_{N}}\;
  \prod_{\yA}{\yRR_{\yA}}^{L\yFF_{\yA}}
\end{equation}
where $\re(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\log(\yFF_{\yA}/\yRR_{\yA})$ is
the relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is the
reference distribution, and $\yL$ a positive parameter. The approximate
equality (obtained through Stirling's approximation), where the large
parentheses denote a multinomial coefficient, shows that this prior belief
is proportional to the number of ways in which the distribution $\yF$ can
be realized in $L$ time bins. The parameter $L$ roughly quantifies how many
time bins our data set must have to affect our initial belief. The
maximum-entropy approximation is valid when $L$ is large, but small
compared to the sharpness of the constraints on $\yF$; in our case this
means $\yL \approx 10$, give or take an order of magnitude.

We could obviously consider pre-data beliefs different
from~\eqref{eq:entropic_prior}, for example one quantified by a Dirichlet
distribution (which is equivalent to the above but with $\yF$ and $\yR$
switched), or a uniform distribution in $\yF$-space. Would these lead to
markedly different post-data beliefs? A full-fledged probabilistic analysis
shows that the three typical features listed above still appear with these
different initial beliefs. They are therefore robust.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-03T09:54:02+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

% \medskip

% The second point is that our degrees of belief about the frequency
% distribution for the larger population depend not only on the measured data in
% the sample, but also on our pre-data beliefs $\yI$ about the distribution.
% Which assumptions lead to the maximum-entropy result? This distribution
% appears when our initial belief about the possible frequency distributions
% $\yF$ is quantified by an entropic prior
% \citep{neumann2007,rodriguez1991,skilling1998,catichaetal2004,portamana2017}:
% \begin{equation}
%   \label{eq:entropic_prior}
%   \pf(\yF \| \yI) \propto  \exp[-\yL\;\re(\yF;\yR)]
%   \approx \binom{L}{L\yFF_{0}, \dotsc, L\yFF_{N}}\;
%   \prod_{\yA}{\yRR_{\yA}}^{L\yFF_{\yA}}
% \end{equation}
% where $\re(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\log(\yFF_{\yA}/\yRR_{\yA})$ is
% the relative entropy or discrimination information
% \citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is the
% reference distribution, and $\yL$ a positive parameter. The approximate
% equality (obtained through Stirling's approximation), where the large
% parentheses denote a multinomial coefficient, shows that this prior belief
% is proportional to the number of ways in which the distribution $\yF$ can
% be realized in $L$ time bins. The parameter $L$ roughly quantifies how many
% time bins our data set must have to affect our initial belief. The
% maximum-entropy approximation is valid when $L$ is large, but small
% compared to the sharpness of the constraints on $\yF$; in our case this
% means $\yL \approx 10$, give or take an order of magnitude.

\mynote{add this above}We could obviously consider pre-data beliefs different
from~\eqref{eq:entropic_prior}, for example one quantified by a Dirichlet
distribution (which is equivalent to the above but with $\yF$ and $\yR$
switched), or a uniform distribution in $\yF$-space. Would these lead to
markedly different post-data beliefs? A full-fledged probabilistic analysis
shows that the three typical features listed above still appear with these
different initial beliefs. They are therefore robust.
